paper1_results_figs_slimmed_50_rr

### 2016-09-12 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
added pruning test
relabel
minor legend tweak

@@

             facet_grid( ~ mixA_not20pc_better_seq0.5, labeller=as_labeller( c('0'='adaptive mix\ntime to resistance\n >20% longer','1'='adaptive mix\ntime to resistance\n >20% longer'))) +

@@

>>>>

  #renaming levels just for fig labels
  levels(ggSubset$strategy) <- c("Mix both","Adaptive both","Sequential both","Mix either")

@@

             facet_grid( ~ mixA_not20pc_better_seq0.5, labeller=as_labeller( c('0'='adaptive mix\ntime to resistance\n >=20% longer','1'='adaptive mix\ntime to resistance\n <=20% longer'))) +

@@

    #test tree pruning, seemed to suggest we are pruning more than needed
    # plotcp(tree)  
    # 
    # cat("optimal cp used in pruning=",cpOptimal,"\n")
